Decision Assistance and Steering in Health Insurance

### 2021-06-14 finals/paper.tex
Updates from Overleaf

@@

\newpage
\begin{figure}[htbp]
\centering
\footnotesize
\begin{minipage}[h]{6in}
\caption[caption]{\textbf{Premium Rating Regions in California}\footnote{Premium rating regions in the California exchange \citep{CARATE2016}. California's 58 counties are divided into 19 rating areas.}}
\centerline{%
    \includegraphics[scale=.45]{finals/pics/CA_Rating_Regions2.jpg}	
}
\label{rating_area_partitions}
\end{minipage}
\end{figure}

>>>>

With regard to metal tier, Figure~\ref{fig:choice-metal} shows that individuals with decision assistance are about 16 percentage points more likely to select a silver tier plan. With xx\% of unassisted households selecting a silver plan, this reflects a relative increase of xx\% in the probability of selecting a silver plan. Most of this increase comes from a reduction in the probability of selecting a bronze plan, with a smaller (but still significant) reduction in selecting gold plans.

@@

\clearpage
\newpage
\begin{figure}[htb]
\centering
\footnotesize
\begin{minipage}[h]{6in}
\caption[caption]{\textbf{Premium Rating Regions in California}\footnote{Premium rating regions in the California exchange \citep{CARATE2016}. California's 58 counties are divided into 19 rating areas.}}
\centerline{%
    \includegraphics[scale=.45]{finals/pics/CA_Rating_Regions2.jpg}	
}
\label{rating_area_partitions}
\end{minipage}
\end{figure}
